---
title: "Incarceration Rates In Santa Clara County"
author: "Claire Lai"
date: "2/19/2022"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r sourcing data, echo = FALSE}
source("../source/analysis.R")
```

## Introduction + Summary Information

As you introduce your report and the dataset, you should describe the variables that you've chosen to analyze. In doing so, make clear which measure(s) of incarceration you are focusing on. 

```{r aapi mean, echo = FALSE}
aapi_mean
aapi_mean_ca
```

## Trends Over Time Chart

In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

```{r trends over time chart, echo = FALSE}
plot(graph1)
```

## Variable Comparison Chart

In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

```{r variable comparison chart, echo = FALSE}

```

## Map

In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

```{r map, echo = FALSE}
plot(map)
```
